\documentclass[]{article}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{imakeidx}
\usepackage{ebgaramond}
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{geometry}
\pdfpagewidth 17 cm
\pdfpageheight 25.3 cm
\usepackage[hidelinks=true]{hyperref}
\usepackage{fontawesome}
\usepackage{changepage}

%Set accent color
\definecolor{accent}{RGB}{97, 114, 31}

%Set bullet point size and color
\newcommand{\mybullet}{\color{accent}\Large$\bullet$}
\newlength{\mylen} \settowidth{\mylen}{\mybullet}
\renewcommand{\labelitemi}{\parbox[c]{\mylen}{\mybullet}}

%Format title page
\begin{document}
\large
\phantomsection\label{rec:Chicken Caesar Salad}
\subsection*{\center\huge Chicken Caesar Salad}\index{Chicken Caesar Salad}\index[prop]{\textbf{Favourites}!Chicken Caesar Salad}\index[prop]{\textbf{Untested}!Chicken Caesar Salad}\index[cuisine]{\textbf{Mexican}!Chicken Caesar Salad}
\begin{description}
\item[Makes:] 4 serves
\item[Cost:] \textdollar4.06 per serve Excluding Iceberg lettuce, Mayonnaise, Dijon mustard, Salt and Pepper
\item[Time:] 60 minutes
\item[Difficulty:] 5/10
\end{description}
\vspace{0.2cm}\hrule\vspace{0.5cm}
\begin{adjustwidth}{0.5 cm}{0.5 cm}

Alledgedly made first by an Italian chef in Mexico. Following the way dad made this at home, but using sauce from \href{https://www.recipetineats.com/chicken-caesar-salad/}{Recipe Tin Eats} and egg technique from \href{https://www.australianeggs.org.au/recipes-and-cooking/easy-boiled-eggs}{Australian Eggs}. \hfill\color{accent}{\Large\hyperref[fig:Chicken Caesar Salad]{\faCameraRetro}\hspace{0.1cm}\faHeart\hspace{0.1cm}\href{https://www.recipetineats.com/chicken-caesar-salad/}{Recipe Tin Eats} and egg technique from \href{https://www.australianeggs.org.au/recipes-and-cooking/easy-boiled-eggs}{\faLink}\hspace{0.1cm}}\color{black}

\end{adjustwidth}
\vspace{0.5cm}\hrule
\subsubsection*{\Large Ingredients}
\begin{multicols}{2}
\begin{itemize}
 \item Chicken thigh \hfill 500 grams
 \item Iceberg lettuce \hfill 0.5 whole (8 cups)
 \item Tomato \hfill 4 whole
 \item Eggs \hfill 4 whole
 \item Bread \hfill 6 whole (slices)
 \item Mayonnaise \hfill 1 cup
 \item Dijon mustard \hfill 2 tsp
 \item Worcestershire sauce \hfill 1 tbsp
 \item Parmesan \hfill 100 grams (0.5 cup grated)
 \item Garlic \hfill 3 cloves
 \item Lemon \hfill 0.5 whole (2 tbsp juiced)
 \item Milk \hfill 3 tbsp
 \item Salt \hfill 0 to taste
 \item Pepper \hfill 0 to taste
\end{itemize}
\end{multicols}
\subsubsection*{\Large Method}
\begin{enumerate}[font=\huge\color{accent}]
	\item Place 2 whole chicken thighs in pan on high heat. Sear and then place lid on, reduce heat if it burns, flip, repeat. Do 2 batches, 2 thighs at a time.
	\item Half fill a medium saucepan with cold water, place eggs in the water and heat on medium until it starts to simmer.
	\item Juice lemon and crush garlic. Mix all sauce ingredients in a bowl.
	\item When eggs are simmering, start a 6 minute timer.
	\item Cut tomato and lettuce into large chunks, wash lettuce.
	\item Prepare a bowl of ice water for eggs.
	\item Remove eggs from heat into ice water, then peel shells and cut into quarters.
	\item Toast bread and cut into 16 pieces per slice.
	\item Combine all ingredients and toss.
\end{enumerate}
\end{document}